Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-01-20 src-latex/parts/20-related-work.tex
Replace forward reference to fig with fwd ref to section.

The directory processing pipeline presented in \cite{bell2020automated} includes an OCR step, done with Tesseract, and a NER step to identify company names and addresses, performed using regular expressions.
This section reviews existing OCR and NER approaches with historical texts and presents some works assessing the effects of OCR quality on the NER performance and the proposed solutions.

\subsection{Optical Character Recognition of historical texts}
Among the large amount of OCR solutions, being either open, free or paid software, available as libraries, Python packages, binaries or cloud API, not all options seem suitable for historical document processing.
We chose to avoid in our study paid and closed-source solutions.
This notably discards Transkribus~\cite{transkribus}, which relies on the commercial system ABBYY's Finereader as well as on two handwritten transcription engines, to process text.
% for Transkribus HTR engines, there is one closed source and one apparently open source
% we should test the open source one: https://github.com/jpuigcerver/pylaia

@@

Based on those works, we chose to test three OCR systems, namely, Tesseract, PERO OCR, and Kraken. We also adopt two deep-learning-based French language models, available in packaged software libraries, already trained for the NER task and that we can adapt to the domain of historical directories: SpaCy NLP pipelines and CamemBERT.
\Cref{fig.pipeline} depicts the evaluation protocol used to assess the combined performance of these OCR and NER systems.

\textbf{Tesseract} is a long-living project, born as a closed-sourced OCR at Hewlett-Packard in the eighties, it was progressively modernized, then open-sourced in 2005. From 2006 until November 2018 it was developed by Google, and is still very active. We used in our tests the version 4.1.1, released Dec. 26, 2019. The version 5, released on Nov. 30, 2021, has not been integrated in our tests yet.

@@

\textbf{\peroocr} is a very recent project (started in 2020) from the Brno University of Technology, in Czech Republic.
Their authors used many state-of-the-art techniques to train it very efficiently.
We used the version from the master branch of their GitHub repository, updated on Sep 15, 2021.
We used the pre-trained weights provided by the authors on the same repository, created on Oct. 9, 2020 from European texts with Latin, Greek and Cyrillic scripts.
% https://github.com/DCGM/pero-ocr
% https://www.fit.vut.cz/~ihradis/pero/pero_eu_cz_print_newspapers_2020-10-09.tar.gz

\textbf{SpaCy} is a software library that offers NLP components assembled in modular pipelines specialised by language.
Although BERT is available in the latest version of SpaCy (v3), the pipeline for French does not provide a NER layer at the time of our experiments (as of january 2022).
Hence, we rely on SpaCy's ad hoc pipeline trained on French corpora and capable of named entity recognition.
% deep-sequoia and wikiner-fr, capable of named entity recognition.\textit{fr\_core\_news\_lg}\footnote{https://spacy.io/models/fr} trained two corpora in French: deep-sequoia and wikiner-fr, capable of named entity recognition.
The global architecture of these pipelines have not been yet published but are explained by the developers on their website.
Words are first encoded into local context-aware embeddings using a window-based CNN similar to~\cite{collobert2011}.
The decision layer is an adaptation of the transition-based model presented in~\cite{lample2016}.
As words are processed sequentially, their vectors are concatenated with those of the last known entities to encode the nearby predicted semantics.
The classification layer relies on a finite-state machine whose transition probabilities are learned using a multi layer perceptron.
% \bertrand{Drop the next sentences if we need space}
% In 2018~\cite{won2018} evaluated SpaCy's NER ability to detect place names in five corpora of ancient letters written in English.
% They measured an average F1 score of 0.57.
% The SpaCy developers claim an accuracy of 0.85 for the English NER pipeline \textit{en\_core\_web\_lg} on the OntoNotes 5.0 corpus\footnote{https://spacy.io/usage/facts-figures}.
%For our experiments, the French model \textit{fr\_core\_news\_lg} is fine-tuned using our ground truth corpus.

\textbf{CamemBERT}
Language model based on \textit{Transformers} \cite{vaswani2017attention}, like BERT \cite{devlin2018bert}, have become a new paradigm for NER\cite{li2020}. 
The learned embeddings can be used as distributed representations for input instead of traditional embeddings like Google Word2Vec, and they can be further fine-tuned for NER by adding an additional output layer. 
They can also be pre-trained in an unsupervised way on historical texts for domain adaptation.
CamemBERT \cite{martin-etal-2020-camembert}, is a well-known French language model derived from BERT, of which there are already trained versions for the NER task on the Huggingface library.

>>>>

The directory processing pipeline presented in \cite{bell2020automated} includes an OCR step, done with Tesseract, and a NER step to identify company names and addresses, performed using regular expressions.
This section reviews existing OCR and NER approaches on historical texts and presents some works assessing the effects of OCR quality on the NER performance and the proposed solutions.

\subsection{Optical Character Recognition of historical texts}
Among the large number of OCR solutions, being either open, free, or paid software, available as libraries, Python packages, binaries, or cloud API, not all options seem suitable for historical document processing.
We chose to avoid in our study paid and closed-source solutions.
This notably discards Transkribus~\cite{transkribus}, which relies on the commercial system ABBYY's Finereader as well as on two handwritten transcription engines, to process text.
% for Transkribus HTR engines, there is one closed source and one apparently open source
% we should test the open source one: https://github.com/jpuigcerver/pylaia

@@

Based on those works, we chose to test three OCR systems, namely, Tesseract, \peroocr, and Kraken. We also adopt two deep-learning-based French language models, available in packaged software libraries, already trained for the NER task and that we can adapt to the domain of historical directories: SpaCy NLP pipelines and CamemBERT.
In \cref{sec:dataset}, we will explain the evaluation protocol used to assess the combined performance of these OCR and NER systems.

\textbf{Tesseract} is a long-living project, born as a closed-sourced OCR at Hewlett-Packard in the eighties, it was progressively modernized, then open-sourced in 2005. From 2006 until November 2018, it was developed by Google and is still very active. We used in our tests version 4.1.1, released Dec. 26, 2019. Version 5, released on Nov. 30, 2021, has not been integrated in our tests yet.

@@

\textbf{\peroocr} is a very recent project (started in 2020) from the Brno University of Technology in Czech Republic.
Their authors used many state-of-the-art techniques to train it very efficiently.
We used the version from the master branch of their GitHub repository, updated on Sep 15, 2021.
We used the pre-trained weights provided by the authors on the same repository, created on Oct. 9, 2020 from European texts with Latin, Greek, and Cyrillic scripts.
% https://github.com/DCGM/pero-ocr
% https://www.fit.vut.cz/~ihradis/pero/pero_eu_cz_print_newspapers_2020-10-09.tar.gz

\textbf{SpaCy} is a software library that offers NLP components assembled in modular pipelines specialised by language.
Although BERT is available in the latest version of SpaCy (v3), the pipeline for French does not provide a NER layer at the time of our experiments (as of January 2022).
Hence, we rely on SpaCy's ad hoc pipeline trained on French corpora and capable of Named Entity Recognition.
% deep-sequoia and wikiner-fr, capable of named entity recognition.\textit{fr\_core\_news\_lg}\footnote{https://spacy.io/models/fr} trained two corpora in French: deep-sequoia and wikiner-fr, capable of named entity recognition.
The global architecture of these pipelines have not been yet published but are explained by the developers on their website.
Words are first encoded into local context-aware embeddings using a window-based CNN similar to~\cite{collobert2011}.
The decision layer is an adaptation of the transition-based model presented in~\cite{lample2016}.
As words are processed sequentially, their vectors are concatenated with those of the last known entities to encode the nearby predicted semantics.
The classification layer relies on a finite-state machine whose transition probabilities are learned using a multi-layer perceptron.
% \bertrand{Drop the next sentences if we need space}
% In 2018~\cite{won2018} evaluated SpaCy's NER ability to detect place names in five corpora of ancient letters written in English.
% They measured an average F1 score of 0.57.
% The SpaCy developers claim an accuracy of 0.85 for the English NER pipeline \textit{en\_core\_web\_lg} on the OntoNotes 5.0 corpus\footnote{https://spacy.io/usage/facts-figures}.
%For our experiments, the French model \textit{fr\_core\_news\_lg} is fine-tuned using our ground truth corpus.

\textbf{CamemBERT} is an adaptation of the BERT transformer-based model for the French language\cite{vaswani2017attention,devlin2018bert}. Such language models have become a new paradigm for NER\cite{li2020}. 
The learned embeddings can be used as distributed representations for input instead of traditional embeddings like Google Word2Vec, and they can be further fine-tuned for NER by adding an additional output layer. 
They can also be pre-trained in an unsupervised way on historical texts for domain adaptation.
CamemBERT \cite{martin-etal-2020-camembert}, is a well-known French language model derived from BERT, of which there are already trained versions for the NER task on the Huggingface library.
